\tool: Revisiting BadUSB with Type-C

### 2021-01-25 WOOT/Files/experiment.tex
revision of case study

Not only does sharing power bank provides convenience to users, but it also brings security issues. 
We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices. 
An attacker are able to modify his/her rented power banks and return it to a power bank station.
Then the next user will unknowingly connect to such a malicious power bank, which endangers his/her financial and data security.

@@

\subsubsection{Attack Scenario}

>>>>

Not only does sharing power bank provides convenience to users, but it also brings security issues. 
We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices. 
An attacker are able to modify his/her rented power banks and return it to a power bank station causing potential threat to subsequent users.

@@

\subsubsection{Attack Scenario}
In this part, we will introduce a real life attack scenario to prove that our \tool is a practical offensive tool.
This scenario can be decomposed into the following steps.
\begin{enumerate}[I. ]
	\item The attacker rents a power bank from any power bank stations and replace the internal components with our \tool.
	\item The attacker returns modified power bank to another power bank station in a crowded area like airport or railway station.
	\item Other users borrows the modified power bank and connects it to their own devices, becoming the victim of \tool.
	\item The attacker now has complete control over victim's device.
\end{enumerate}
